NEW TITLE

### 2019-11-01 paper.tex
Minor fix in text to describe the 3 settings

A set of bone-conduction headphones is used as the audio transmission medium.
These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
=======
This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.

@@

The pitch is changed as a linear function of the elevation angle and the gradient is determined by setting the angle and pitch limits.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
After practical tests with the interface, we set the neutral pitch to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
We set the pitch limits to 2 octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
The linear function is visualised in \cref{fig:pitch-gain}.

@@

>>>>

A set of bone-conduction headphones is used as the audio transmission medium.
These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.

@@

The pitch is changed as a linear function of the elevation angle and the gradient is determined by setting the angle and pitch limits.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
After practical tests with the interface, we set the neutral, on-target pitch the HMI emits to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.

@@

As part of this experiment, we wanted to see how changing the gradient of the pitch function affected target acquisition performance, e.g.\ does a steeper pitch gain function as a function of the elevation angle improve accuracy or decrease the search time?
Pitch limits of 1, 2 and 3 octaves above and below the neutral tone was then set of the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively.
These linear gain functions are visualised in \cref{fig:pitch-gain}.
